The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-26 article.tex
Benchmark fpgen --type=path and convert -ofmt=smi rerun for 2.0 now patches have been applied, simplifies explanation of why there were skipped entires.
Add footnote on he MDL parity value, not sure if there's a better way to fit in this digression.

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates can optionally identify
  perspective projections, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently considered distinct can be merged
  (Figure~\ref{fig:stereoprojections}).  The perception is based on an  algorithm briefly  
  described by~\cite{Karapetyan2015}.

@@

Assigning double-bond configurations in SMILES is 
non-trivial and \cdkversion{} has some safety checks, since the SMILES output is 
Keklu$\mathrm{\acute{e}}$ but input was aromatic, when the bond orders are 
assigned an extra double-bond may be accidental encoded in the SMILES output, 
this is sometimes acceptable but will currently report an error. A few errors (4
in ChEBI, 3 in ChEMBl) occur from Sgroup processing that have now been addressed.

@@

\textbf{-type path}: Path based fingerprints encode paths of length 1...n. n was
choose to be 6 for this benchmark. Path based fingerprints can be used for both
substructure and similarity screening. The algorithm was
tweaked for \cdkversion{} to hash the paths without pre-computing all paths
upfront and without needing to generate character strings before hashing. An
abort threshold was also placed to catch pathological molecules (shown as 
skipped in ChEBI) that previously took a long time - this will be optimized and 
removed in future. The time to encode ChEMBL previously took 26-35 minutes now 
only takes $\sim$5 minutes.

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt smi}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 35.63s & 68.4K & 16 & 1.37s & 1.8M & 26.01\\
 &  & sdf & 35 & 20.91s & 122.5K & 29 & 4.21s & 608.6K & 4.97\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 14m26.02s & 116.3K & 34 & 28.65s & 3.5M & 30.23\\
 &  & sdf & 0 & 8m59.38s & 186.7K & 4 & 1m27.35s & 1.2M & 6.17\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 1m14.5s & 32.7K & 26 & 8.22s & 296.3K & 9.06\\
 &  & sdf & 0 & 1m52.17s & 22.8K & 40 & 11.67s & 219.6K & 9.61\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 35m2.8s & 47.9K & 9 & 5m35.25s & 300.4K & 6.27\\
 &  & sdf & 0 & 38m51.73s & 43.2K & 0 & 6m7.04s & 274.4K & 6.35\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt smi}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 13.12s & 185.7K & 7 & 0.4s & 6.1M & 32.8\\
 &  & sdf & 35 & 13.7s & 187K & 4 & 0.46s & 5.6M & 29.8\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 14 & 5m46.72s & 290.4K & 25 & 16.48s & 6.1M & 21\\
 &  & sdf & 0 & 5m42.09s & 294.4K & 4 & 20.12s & 5M & 17\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 51.99s & 46.9K & 17 & 7.25s & 336K & 7.2\\
 &  & sdf & 0 & 1m44.96s & 24.4K & 15 & 7.92s & 323.5K & 13.3\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 26m23.5s & 63.6K & 0 & 5m23.08s & 311.7K & 4.9\\
 &  & sdf & 0 & 35m34.44s & 47.2K & 0 & 4m59.81s & 335.9K & 7.1\\

>>>>

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile\footnote{Molfiles 
  can also store tetrahedral stereochemistry as a parity value, this is read if no coordinates are specified.
  In general there is no guarantee the parity value is read and the only portable way to store
  stereochemistry in a molfile is with coordinates.}, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates 
  can optionally identify
  perspective projections, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently considered distinct can be merged
  (Figure~\ref{fig:stereoprojections}).  The perception is based on an  algorithm briefly  
  described by~\cite{Karapetyan2015}.

@@

Assigning double-bond configurations in SMILES is 
non-trivial and \cdkversion{} has some safety checks, since the SMILES output is 
Keklu$\mathrm{\acute{e}}$ but input was aromatic, when the bond orders are 
assigned an extra double-bond may be accidental encoded in the SMILES output, 
this is sometimes acceptable but will currently report an error.

@@

\textbf{-type path}: Path based fingerprints encode paths of length 1...n. n was
choose to be 6 for this benchmark. Path based fingerprints can be used for both
substructure and similarity screening. The algorithm was
tweaked for \cdkversion{} to hash the paths without pre-computing all paths
upfront and without needing to generate character strings before hashing. The 
time to encode ChEMBL previously took 26-35 minutes now only takes $\sim$5 
minutes.

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt smi}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 35.63s & 68.4K & 16 & 1.6s & 1.5M & 22.27 \\
 &  & sdf & 35 & 20.91s & 122.5K & 25 & 4.47s & 573.2K & 4.68 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 14m26.02s & 116.3K & 34 & 28.14s & 3.6M & 30.78 \\
 &  & sdf & 0 & 8m59.38s & 186.7K & 1 & 1m19.86s & 1.3M & 6.75 \\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 1m14.5s & 32.7K & 9 & 8.67s & 280.9K & 8.59 \\
 &  & sdf & 0 & 1m52.17s & 22.8K & 25 & 12.15s & 210.9K & 9.23 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 35m2.8s & 47.9K & 9 & 5m31.52s & 303.8K & 6.34 \\
 &  & sdf & 0 & 38m51.73s & 43.2K & 0 & 6m19.63s & 265.3K & 6.14 \\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt smi}}  & \multirow{2}{*}{ChEBI 149} & smi & 0 & 13.12s & 185.7K & 7 & 0.63s & 3.9M & 20.8 \\
 &  & sdf & 35 & 13.7s & 187K & 0 & 0.72s & 3.6M & 19 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 5m46.72s & 290.4K & 25 & 15.97s & 6.3M & 21.7 \\
 &  & sdf & 0 & 5m42.09s & 294.4K & 1 & 12.63s & 8M & 27.1 \\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 51.99s & 46.9K & 0 & 7.7s & 316.3K & 6.8 \\
 &  & sdf & 0 & 1m44.96s & 24.4K & 0 & 8.4s & 305K & 12.5 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 26m23.5s & 63.6K & 0 & 5m19.35s & 315.3K & 5 \\
 &  & sdf & 0 & 35m34.44s & 47.2K & 0 & 5m12.4s & 322.4K & 6.8 \\
